RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-08-21 manuscripts/manuscript.Rmd
added link to treebase where first mentioned

The ability to read in phylogenetic trees in the NeXML format opens up a
wide and rapidly growing array of resources to the R user.  For instance,
a user can access all the phylogenies available in TreeBASE <!-- first mention -->
<!-- of TreeBase, include URL? or introduce it in intro? --> through the
`nexml` format.  `RNeXML` can read directly from a URL:

>>>>

The ability to read in phylogenetic trees in the NeXML format opens up a
wide and rapidly growing array of resources to the R user.  For instance,
a user can access all the phylogenies available in 
[TreeBASE](http://treebase.org/treebase-web/home.html) <!-- first mention -->
<!-- of TreeBase, include URL? or introduce it in intro? --> through the
`nexml` format.  `RNeXML` can read directly from a URL:
